ms_figures

### 2023-02-07 ms_figures.Rmd

```{r fig4a}
diversity <- read.csv("/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv")
fig4a <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

@@

```{r fig4b}
fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Domestic" = "shannon_domestic", "Foreign" = "shannon_foreign") %>% 
  pivot_longer(Domestic:Foreign, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Domestic", "Foreign"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[2], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

fig4c
```

```{r fig4d}
fig4d_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4d <- fig4d_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = imports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "")

@@

fig4d
```
```{r fig4e}
fig4e_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4e <- fig4e_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = exports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total exports (million t, live weight)",
       y = "Supply diversity",
       color = "")

@@

fig4e
```

```{r fig4, fig.height = 7, fig.width = 7}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

@@

```{r si_top_exporters, fig.height = 12, fig.width = 5}

@@

```{r si_top_importers, fig.height = 12, fig.width = 5}

@@

importers_old_plot <- top_importers_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importers_recent_plot <- top_importers_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(
  importers_old_plot,
  importers_recent_plot,
  ncol = 2,
  labels = c("Old", "Recent")
)

@@

```{r si_regional_changes, fig.height = 12, fig.width = 5}

@@

```{r si_export_decreases_increases, fig.height = 12, fig.width = 5}
top_export_increases <- read.csv(file.path(datadir, "top_export_increases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_export_decreases <- read.csv(file.path(datadir, "top_export_decreases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

@@

```{r si_import_decreases_increases, fig.height = 12, fig.width = 5}
top_import_increases <- read.csv(file.path(datadir, "top_import_increases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_import_decreases <- read.csv(file.path(datadir, "top_import_decreases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

@@

```{r regional_avg_annual_change, fig.height = 10, fig.width = 6}
regional_avg_annual_change <- read.csv(file.path(datadir, "regional_avg_annual_change.csv"))

@@

regional_slopes_ranked
```

@@

ldc_net_exports_by_source_plot
```

>>>>

```{r fig4a}
diversity <- read.csv("/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv")
fig4a <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        text = element_text(size = 18)
        )

@@

```{r fig4b}
fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Domestic" = "shannon_domestic", "Foreign" = "shannon_foreign") %>% 
  pivot_longer(Domestic:Foreign, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Domestic", "Foreign"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[2], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        text = element_text(size = 18))

```{r fig4c}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4c <- fig4c_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = imports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "") +
  theme(
    text = element_text(size = 18)
  )

@@

fig4c
```
```{r fig4d}
fig4d_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4d <- fig4d_data %>%
  # total supply greater than 1 tonne (FIXIT update manuscript caption)
  filter(supply > 1) %>%
  ggplot(aes(x = exports/1000000, y = shannon_supply, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  annotation_logticks(sides = "b") +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total exports (million t, live weight)",
       y = "Supply diversity",
       color = "") +
  theme(
    text = element_text(size = 18)
  )

@@

fig4d
```

```{r fig4, fig.height = 5, fig.width = 7}
fig4 <- ggarrange(
  ggarrange(
    fig4a, fig4b,
    ncol = 1,
    nrow = 2,
    labels = c("a", "b")
  ),
  ggarrange(
    fig4c, fig4d,
    ncol = 1,
    nrow = 2,
    common.legend = TRUE,
    legend = "bottom",
    labels = c("c", "d")
  ),
  nrow = 1, ncol = 2,
  widths = c(1, 0.5)
)

```{r fig4_old, fig.height = 7, fig.width = 7}
fig4 <- ggarrange(fig4a,
                  fig4b,
          ggarrange(fig4d,
                    fig4e,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("c", "d")),
          nrow = 3,
          labels = c("a", "b", "")
          )

@@

```{r si_top_exporters, fig.height = 5, fig.width = 4}

@@

```{r si_top_importers, fig.height = 5, fig.width = 4}

@@

importers_old_plot <- top_importers_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  xlim(c(0, 5.5)) +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importers_recent_plot <- top_importers_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = reorder(importer_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  xlim(c(0, 5.5)) +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(
  importers_old_plot,
  importers_recent_plot,
  ncol = 2,
  labels = c("'96-'00", "'16-'20")
)

@@

```{r si_regional_changes, fig.height = 4, fig.width = 4}

@@

```{r si_export_decreases_increases, fig.height = 4, fig.width = 4.5}
top_export_increases <- read.csv(file.path(datadir, "top_export_increases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_export_decreases <- read.csv(file.path(datadir, "top_export_decreases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

@@

```{r si_import_decreases_increases, fig.height = 4, fig.width = 4.5}
top_import_increases <- read.csv(file.path(datadir, "top_import_increases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))
top_import_decreases <- read.csv(file.path(datadir, "top_import_decreases.csv")) %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown")))

@@

```{r regional_avg_annual_change, fig.height = 4, fig.width = 5}
regional_avg_annual_change <- read.csv(file.path(datadir, "regional_avg_annual_change.csv"))

@@

regional_slopes_ranked

ggsave(file.path(outdir, "regional_avg_annual_change.png"))
```

@@

ldc_net_exports_by_source_plot

ggsave(file.path(outdir, "ldc_net_exports_by_source.png"))
```
